---
title: "FIFA18"
author: "Kesong Wu"
date: "2018/4/29"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
```

##Introduction

We will use the statistical information of football plyers inthe video game FIFA 18.

#Load the data and Clean the data
There are three tables we may use in this project.
```{r load, echo=FALSE}
ppd <- read.csv("PlayerPersonalData.csv", header = TRUE)
# Player's Personal Data
ppp <- read.csv("PlayerPlayingPositionData.csv", header = TRUE)
# Player's Playing Position Data
pad <- read.csv("PlayerAttributeData.csv", header = TRUE)
# Player's Attribute Data
```

Let's have a glimpse on the data.
```{r glimpse, echo=FALSE}
glimpse(ppd)
glimpse(ppp)
glimpse(pad)
```

From the glimpse we can find that every table has useless columns and there is a column called "index" that can join the three tables together.
```{r join, echo=FALSE}
fifa <- ppd[,-c(1:2)] %>%
  full_join(ppp[,-1], by = "ID") %>%
  full_join(pad[,-1], by = "ID")

kable(head(fifa))
```

##Ages of football players

Let's have a look at the density of the ages of these football player.
```{r ages, echo=FALSE}
ggplot(fifa, aes(Age)) + geom_density()
```