---
title: "FIFA18"
author: "Kesong Wu"
date: "2018/4/29"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(rworldmap)
library(tidyverse)
library(corrplot)
```

##Introduction

We will use the statistical information of football plyers inthe video game FIFA 18.

##Load the data and Clean the data
There are three tables we may use in this project.
```{r load, echo=FALSE}
ppd <- read.csv("PlayerPersonalData.csv", header = TRUE)
# Player's Personal Data
ppp <- read.csv("PlayerPlayingPositionData.csv", header = TRUE)
# Player's Playing Position Data
pad <- read.csv("PlayerAttributeData.csv", header = TRUE)
# Player's Attribute Data
```

Let's have a glimpse on the data.
```{r glimpse, echo=FALSE}
dim(ppd)
glimpse(ppd)
dim(ppp)
glimpse(ppp)
dim(pad)
glimpse(pad)
```

From the glimpse we can find that every table has useless columns and there is a column called "index" that can join the three tables together.
```{r join, echo=FALSE}
fifa <- ppd[,-c(1:2)] %>%
  full_join(ppp[,-1], by = "ID") %>%
  full_join(pad[,-1], by = "ID")

dim(fifa)
# From the dim, we can see that there may be some dupicate rows in our data
fifa <- fifa[!duplicated(fifa$ID),]

kable(head(fifa))
```

##Ages of football players

Let's have a look at the density of the ages of these football player.
```{r ages, echo=FALSE}
ggplot(fifa, aes(Age)) + geom_density()
```

From this plot we can see that most players are between 18 and 30.

##Player's Overall

Let's see how the overall scores of all the players are distribute.
```{r overall, echo=FALSE}
fifa %>%
  ggplot(aes(x = Overall, fill = factor(Overall))) + geom_bar() + ggtitle("Player's Overall") + theme(plot.title = element_text(hjust = .5)) + guides(fill = FALSE)
# Use guides(fill = FALSE) to avoid messing up the plot
```

Then let's see if overall scores are related to players' ages.
```{r ova, echo=FALSE}
fifa %>%
  ggplot(aes(x = Age, y = Overall)) + geom_point() + geom_smooth(span = 1) 
```

We can see that the players are improving with the step of the years. The best players are 30 years old and after that they start to decline.

##Best Players & Clubs
Based on the overall score, we will find which are the best ten players.
```{r bestplayer, echo=FALSE}
fifa %>%
  arrange(desc(Overall)) %>%
  select(Name, Overall, Club) %>%
  head(10)
```

Then, let's have a look at each team's best player's overall, worst player's overall and the average overall.
```{r teamplayer, echo=FALSE}
TeamPower <- fifa %>%
  select(Name, Club, Overall) %>%
  group_by(Club) %>%
  summarise(Best = max(Overall), Worst = min(Overall), Ave = mean(Overall)) %>%
  arrange(desc(Ave))

TeamPower
```

We can see that the best three clubs are FC Barcelona, Juventus and Real Madrid CF.

##Players who earned most and Clubs paid most
```{r wage, echo=TRUE}
fifa$Wage <- gsub("???", "", fifa$Wage)
fifa$Wage <- gsub("K", "e+03", fifa$Wage)
fifa$Wage <- as.numeric(fifa$Wage)

fifa %>%
  select(Name, Wage, Club) %>%
  arrange(desc(Wage)) %>%
  head(10)

# p.s. I found an interesting here, when I open my file in my R project, I can get the right result in chunk, but when I knit this file, html cannot encode right and I will get all NAs. However, if I do not open it in my R project, it can get the right result both in chunk and html. I tried change my R project's encoding option, but it still didn't work. Why this happen?
```

We can see that, C.Ronaldo and Messi earned most.
```{r teamwage, echo=FALSE}
TeamWage <- fifa %>%
  select(Name, Wage, Club) %>%
  group_by(Club) %>%
  summarise(TotalWage = sum(Wage)) %>%
  arrange(desc(TotalWage))

TeamWage
```
We can see that FC Barcelona, Real Madrid CF and Manchester United paid most.

Let's combine this result with the best teams result we studied before.
```{r pvw, echo=FALSE, warning=FALSE}
TeamPower %>%
  full_join(TeamWage, by = "Club") %>%
  ggplot(aes(x = TotalWage, y = Ave)) + geom_point() + geom_smooth()
```

From this plot, we can easily see that, to be a better team, you have to pay more money.

##Players' Value

We can see that many players might sign a cheap contract before, we now study there value. _We can use sciece notation here._
```{r playervalue, echo=FALSE}
fifa$Value <- gsub("???", "",fifa$Value)
fifa$Value <- gsub("M", "e+06",fifa$Value)
fifa$Value <- gsub("K", "e+03",fifa$Value)
fifa$Value <- as.numeric(fifa$Value)

fifa %>%
  select(Name, Club, Value) %>%
  arrange(desc(Value)) %>%
  head(10)
```
We can see Neymar valued most instead of C.Ronaldo and Messi.

Our table seems better now, and we can output a new csv file for future use.
```{r output, echo=TRUE}
write.csv(fifa, file = "FIFA18.csv")
```

##Nationalities of the Players

Here we use a new package called "rWorldMap" to show the players' nationalitites in a world map.
```{r worldmap, echo=FALSE}
nation <- fifa %>%
  group_by(Nationality) %>%
  summarise(n = n())

prepare <- joinCountryData2Map(dF = nation, joinCode = "NAME", nameJoinColumn = "Nationality", verbose = FALSE)

mapCountryData(mapToPlot = prepare, nameColumnToPlot = "n", catMethod = "fixedWidth",
               oceanCol = "steelblue1", missingCountryCol = "white", 
               mapTitle = "Number of Players by Country", aspect = "variable")
```

We can see that China has no players in these clubs, European countries and South American countries have the most players.
```{r nation, echo=FALSE}
nation %>%
  arrange(desc(n)) %>%
  head(10)
```
These are the countries have most players.

##Players' Last Name

At this part, I just wanna practice the ^Regular Expression^, but in the data we have, Name is the only part we could use. However, many players' first names were not given, for example, "Leonardo Messi" is just given as "L.Messi", so I decided to extract these players' last name.
```{r lastname, echo=FALSE}
name <- fifa$Name
LMEx <- "[A-Z]{1}[a-z]+$"
LastName <- str_extract_all(name, LMEx, simplify = TRUE)

LastName <- as.data.frame(LastName)
colnames(LastName) <- c("name")
LastName %>%
  group_by(name) %>%
  summarise(n = n())%>%
  arrange(desc(n)) %>%
  head(10)
```
For there are many names that are not English letters, we will get many missing values in this progress. 

From the result we can see that the most common last name in FIFA18 football players is _"Silva"_.

##Player's Postion

We can see many players prefer several positions, let's get the positions separated first.
```{r postion, echo=FALSE}
position <- fifa %>%
  select(Name, Preferred.Positions) %>%
  separate(Preferred.Positions, into = c("P1", "P2", "P3", "P4"), sep = " ") 

position %>%
  head(20)
```

Then let's have a look at how many kinds of positions there are an count how many positions each player can play.
```{r numposition, echo=FALSE}
pplay <- position %>%
  select(P1:P4) %>%
  as.matrix() %>%
  as.vector() %>%
  table()

pplay <- pplay[-1]
# delete the data saved as ""

pplay

allposition <- as.data.frame(pplay)[,1]
# save all kinds of positions

position %>%
  mutate(npos = P1 %in% allposition + P2 %in% allposition +P3 %in% allposition + P4 %in% allposition) %>%
  arrange(desc(npos)) %>%
  head(20)
# I think this part I can use "apply" funcion to make it more simple, but I tried many times and did not work
```
We can see that most players prefer playing CB, CM and ST, fewest prefer LWB and RWB. Many players can play four positions.

That surprised me is that, 2024 players prefer GK(Goal Keeper).

```{r combine, echo=TRUE}
combine <- position %>%
  select(P1:P4) %>%
  table()

# p.s. Is there a better way to calculate which pair of positions appear together most times?
```
From the table we can see that the the postions player select together, though not exactly the same, have many characters in common. For example, CB(Center Back) and CM(Center Mid-fielder), nearly the same position.

##Simple Analysis

Then let's do some simple analysis based on the data.

There may be some relations between player's value, wage, overall and potential.
```{r cor, echo=FALSE}
fifa %>%
  select(Value, Wage, Overall, Potential) %>%
  cor() %>%
  corrplot()
```